[Artifact57] Robust Resource Bounds with\\ Static Analysis and Bayesian Inference

### 2024-03-29 reviews/response_reound1.md

Thank you all for the feedback.

# Review A

Thank you for taking the time to run all Python scripts. We are happy that you
did not encounter any technical issues with the artifact.

# Review B

Thank you for going through the getting-started guide. We are happy that you did
not encounter any technical issues with the artifact.

# Review C

> The binary included in the docker image crashes immediately (Illegal
> instruction (core dumped)) on my architecture (described below to ease
> debugging).

Thank you for reporting this issue. We suspect that the Docker container
requires an instruction that your computer does not support. We built the docker
image on the OS Ubuntu 22.04 LTS and the CPU Intel(R) Core(TM) i7-7600U CPU @
2.80GHz.

We could not identify the root cause of the issue. So could you please run the
artifact by cloning the GitHub repository and building a Docker image locally on
your machine? We are happy that at least you successfully built the image on
your machine.

> It would be good to add instructions in the README to recompile the code
> directly inside the docker, and avoid those crashes. This would additionally
> allow user to tweak the code directly inside the docker, and observe changes
> there.

Thank you for the suggestion. Technically, from the Dockerfile in the GitHub
repository, one can learn how to recompile the code inside the Docker container.

In the revision of `README.pdf`, we will provide details on how to recompile (i)
the C++ code of the volesti-RaML interface and (i) the OCaml code of Hybrid
RaML. The remaining code, such as the Python scripts, does not need
recompilation after modification.

> Being able to test to analyser on new benchmarks is required to grant the
> "Reusable" badge. It would be helpful to add a small paragraph in the README
> instructing how to do so, and include tools in the docker image to make this
> process easier.

If the user wishes to analyze their custom OCaml program using Hybrid RaML, the
user should first prepare (i) the source file of their OCaml program, augmented
with a list of inputs for runtime cost data generation and (ii) a configuration
file specifying hyperparameters of Hybrid AARA. To learn the formats of these
files, the user can look at the examples inside the artifact. Finally, The user
runs Hybrid RaML as demonstrated in Section 1 of `README.pdf`.

We will explain this point in the revision of `README.pdf`.

> It would improve the artifact to include an editor.

We will install the text editor Vim in the updated Docker image. Alternatively,
if the user wishes to install a different text editor, while the Docker
container is running, the user can run `apt update && apt install <editor-name>
-y` inside the container.

> Should input_dataset be entered manually by the users on each new benchmark?
> Are scripts provided to generate them automatically?

The artifact already comes with a Python script (`input_data_generation.py`
inside the directory `home/hybrid_aara/benchmark_suite/toolbox/`) for generating
lists, pairs of lists (for the benchmark MapAppend), and nested lists (for the
benchmark Concat). For example, the function `create_exponential_lists` inside
this script generates lists whose sizes grow exponentially (e.g., 1, 2, 4, 8,
16, etc.). Here, the initial size (i.e., 1) and exponent (i.e., 2) are specified
by the user. The content of each list is determined randomly. The function
`convert_lists_python_to_ocaml` then converts a list from the Python format to
the OCaml format.

We will mention this Python script in the revised `README.pdf`. Also, we will
revise the script such that, when the user runs `python3
input_data_generation.py`, the script prints out an example collection of input
lists used for runtime cost data generation.

### 2024-03-29 reviews/response_reound1.md

We could not identify the root cause of the issue. So could you please run the
artifact by cloning the GitHub repository and building a Docker image locally on
your machine? We are happy that at least you successfully built the image on
your machine.

> It would be good to add instructions in the README to recompile the code
> directly inside the docker, and avoid those crashes. This would additionally
> allow user to tweak the code directly inside the docker, and observe changes
> there.

Thank you for the suggestion. Technically, from the Dockerfile in the GitHub
repository, one can learn how to recompile the code inside the Docker container.

In Section 4.4 of the revised `README.pdf`, we provide details on how to
recompile (i) the C++ code of the volesti-RaML interface and (i) the OCaml code
of Hybrid RaML. The remaining code, such as the Python scripts, does not need
recompilation after modification.

@@

> Being able to test to analyser on new benchmarks is required to grant the
> "Reusable" badge. It would be helpful to add a small paragraph in the README
> instructing how to do so, and include tools in the docker image to make this
> process easier.

If the user wishes to analyze their custom OCaml program using Hybrid RaML, the
user should first prepare (i) the source file of their OCaml program, augmented
with a collection of inputs for generating runtime cost data and (ii) a
configuration file specifying hyperparameters of Hybrid AARA. To learn the
formats of these files, the user can look at the examples inside the artifact.
Finally, The user runs Hybrid RaML as demonstrated in Section 1 of `README.pdf`.

In Section 4.3 of the revised `README.pdf`, we explain this point.

@@

We will install the text editor Vim in the updated Docker image. Alternatively,
if the user wishes to install a different text editor, while the Docker
container is running, the user can run `apt update && apt install <editor-name>
-y` inside the container.

> Should input_dataset be entered manually by the users on each new benchmark?
> Are scripts provided to generate them automatically?

The artifact already comes with a Python script (`input_data_generation.py`
inside the directory `home/hybrid_aara/benchmark_suite/toolbox/`) for generating
lists, pairs of lists (for the benchmark MapAppend), and nested lists (for the
benchmark Concat). For example, the function `create_exponential_lists` inside
this script generates lists whose sizes grow exponentially (e.g., 1, 2, 4, 8,
16, etc.). Here, the initial size (i.e., 1) and exponent (i.e., 2) are specified
by the user. The content of each list is determined randomly. The function
`convert_lists_python_to_ocaml` then converts a list from the Python format to
the OCaml format.

In Section 4.3 of the revised `README.pdf`, we mention this Python script. Also,
we will revise the script such that, when the user runs `python3
input_data_generation.py`, the script prints out an example collection of input
lists used for runtime cost data generation.

### 2024-03-29 README/getting_started_guide.tex
Fixed a typo
Revised README according to the feedback

Load a Docker image by running
\begin{verbatim}
$ docker load --input hybrid_aara.tar.gz
\end{verbatim}
%
It creates an image named \texttt{hybrid\_aara} and stores it locally on your
machine.
%
On some platforms (e.g., macOS), Docker may create an image with a slightly
different name from \texttt{hybrid\_aara}.
%
You can check the name of the image by running \verb|$ docker ps|, which will
display a list of images on your local machine.

@@

\subsection{Example Program}

@@

The configuration file \texttt{config\_bayeswc.json} for \BayesWC{} specifies
(i) the probabilistic model hyperparameter $\gamma_0$ in Weibull survival
analysis\footnote{See Appendix~C of the updated version of the paper. The
probabilistic model is also explained in this PyMC tutorial:
\url{https://www.pymc.io/projects/examples/en/2022.12.0/survival_analysis/bayes_param_survival_pymc3.html}.}
and (ii) the inference hyperparameters such as the number of chains and the
number of iterations to run in a sampling-based Bayesian inference algorithm.

>>>>

Load a Docker image by running
\begin{verbatim}
$ docker load --input hybrid_aara.tar.gz
\end{verbatim}
%
It creates an image named \texttt{hybrid\_aara} and stores it locally on your
%
Docker may create an image with a slightly different name from
\texttt{hybrid\_aara}.
%
You can check the name of the image by running \verb|$ docker images|, which
will display a list of images on your local machine.

@@

\subsection{Example Program}
\label{sec:Example Program}

@@

The configuration file \texttt{config\_bayeswc.json} for \BayesWC{} specifies
(i) the probabilistic model hyperparameter $\gamma_0$ in Weibull survival
analysis\footnote{See Appendix~B of the updated version of the paper. The
  probabilistic model is also explained in this PyMC tutorial:
  \url{https://www.pymc.io/projects/examples/en/2022.12.0/survival_analysis/bayes_param_survival_pymc3.html}.}
and (ii) the inference hyperparameters such as the number of chains and the
number of iterations to run in a sampling-based Bayesian inference algorithm.

### 2024-03-29 README/step_by_step_instructions.tex
Updated the explanation of hyperparameters
Revised README according to the feedback

The table of analysis time produced by the artifact looks different from the one
in the submitted version of the paper, in terms of both the numbers and layout.
%
This is because, since the submission, we have changed the configuration of
sampling-based Bayesian inference algorithms and rerun experiments.
%
In the camera-ready version of the paper, we will update the analysis time in
Table~1.

@@

For example, to perform Hybrid AARA on the benchmark \texttt{QuickSort} using
purely data-driven resource analysis, run
\begin{verbatim}
# python3 run_experiment.py QuickSort data_driven
\end{verbatim}
%
It runs Data-Driven \Opt{}, Data-Driven \BayesWC{}, and Data-Driven \BayesPC{}.
%
The analysis should finish within 2 minutes.
%
If we instead want to perform hybrid resource analysis,
\begin{verbatim}
# python3 run_experiment.py QuickSort hybrid
\end{verbatim}
%
It runs Hybrid \Opt{}, Hybrid \BayesWC{}, and Hybrid \BayesPC{}.
%
The analysis should finish in 11 minutes.
%
To run both purely data-driven and hybrid resource analyses on the benchmark
\texttt{QuickSort}, run
\begin{verbatim}
# python3 run_experiment.py QuickSort
\end{verbatim}
without specifying the analysis mode.

@@

\subsection{Source Code}

Our artifact contains three tools that we have built by ourselves: (i) Hybrid
RaML (in OCaml), (ii) the volesti-RaML interface (in C++), and (iii) the
execution and analysis of benchmark suite (in Python).
%
Their source code is stored in directories \texttt{raml},
\texttt{volesti\_raml\_interface}, and \texttt{benchmark\_suite} inside the
project directory \texttt{/home/hybrid\_aara} in the Docker image.

The project directory contains two additional directories that come from other
sources.
%
The third-party C++ library volesti\footnote{Available here:
  \url{https://github.com/GeomScale/volesti}.} is stored in the directory
\texttt{volesti}.
%
The linear-program solver COIN-OR CLP\footnote{Available here:
  \url{https://github.com/coin-or/Clp}.} is stored in the directory \texttt{clp}.

The code for building a Docker image is available on GitHub:
\url{https://github.com/LongPham7/hybrid_aara_artifact}.
%
To build a Docker image, clone the GitHub repository and then run (in the root
directory)
\begin{verbatim}
$ docker build -t hybrid_aara .
\end{verbatim}
%
We need a period at the end of the command to indciate that Dockerfile exists in
the current working directory.
%
The build will take 20--30 minutes.
%
The resulting image is named \texttt{hybrid\_aara} and is stored locally on your
machine.

To run the image \texttt{hybrid\_aara}, run
\begin{verbatim}
$ docker run --name hybrid_aara -it --rm hybrid_aara
\end{verbatim}
%
If you want to save the image as a tar archive and compress it, run
\begin{verbatim}
$ docker save hybrid_aara | gzip > hybrid_aara.tar.gz
\end{verbatim}

>>>>

The table of analysis time produced by the artifact looks different from the one
in the submitted version of the paper, in terms of both the numbers and layout.
%
This is because, since the submission, we have changed the hyperparameters of
Bayesian inference and rerun experiments.
%
In the camera-ready version of the paper, we will update the analysis time in
Table~1.

@@

For example, to perform Data-Driven \Opt{} on the benchmark \texttt{QuickSort},
run
\begin{verbatim}
# # python3 run_experiment.py QuickSort data_driven opt
\end{verbatim}
%
The analysis should finish in 15 seconds.
%
To perform all data-driven resource analyses on the benchmark
\texttt{QuickSort}, run
\begin{verbatim}
# python3 run_experiment.py QuickSort data_driven
\end{verbatim}
%
It runs Data-Driven \Opt{}, Data-Driven \BayesWC{}, and Data-Driven \BayesPC{}.
%
The analysis should finish within 2 minutes.
%
If we instead want to perform all hybrid resource analyses, replace
\texttt{data\_driven} with \texttt{hybrid}:
\begin{verbatim}
# python3 run_experiment.py QuickSort hybrid
\end{verbatim}
%
It runs Hybrid \Opt{}, Hybrid \BayesWC{}, and Hybrid \BayesPC{}.
%
The analysis should finish in 11 minutes.
%
To run both purely data-driven and hybrid resource analyses on the benchmark
\texttt{QuickSort}, run
\begin{verbatim}
# python3 run_experiment.py QuickSort
\end{verbatim}
without specifying the analysis mode.

@@

### 2024-03-29 README/what_is_included.tex
Revised README according to the feedback

\emph{\textbf{Note:} The tables and plots produced by the artifact are
  slightly different from the ones in the submitted version of the
  paper.
%
  This is because, since the submission, we have adjusted the
  hyperparameters for \BayesWC{} and \BayesPC{} using an automatic
  procedure for choosing hyperparameters.
%
  The updated experiments results still preserve all key findings in
  Section~7 of the paper.
%
  The updated version of the paper accompanies the artifact.}

>>>>

\emph{\textbf{Note:} The tables and plots produced by the artifact are slightly
  different from the ones in the submitted version of the paper.
  %
  This is because, since the submission, we have adjusted the hyperparameters
  for \BayesWC{} and \BayesPC{} using an automatic procedure for choosing
  hyperparameters (Appendix~B of the paper), as requested by the paper
  reviewers.
  %
  The updated experiments results still preserve all key findings in Section~7
  of the paper.
  %
  The updated version of the paper accompanies the artifact.}
